Møil: A web-based administration tool for mail servers backed by relational databases

### 2014-07-30 doc/study/study.tex
Removed last TODOs.

@@

			\todo{Sources for most of the criteria!}

@@

			\subsubsection{Security \& robustness (3)}
			\todo{Password hashing algorithms strengths}
				For now, only three criteria in this category shall be
				considered, because further security analysis would require an
				in-depth source code review. The \crit{password hashing}{3.1}
				availability and algorithm strength is important against
				unauthorized database access through potential security holes
				in the application. When the database is maliciously read, the
				value of the passwords to the attacker is inversely
				proportional to the time it costs, to crack the password
				hashing. \crit{Test coverage}{3.2} is important for this
				evaluation and for security purposes, because it lowers the
				probability of bugs per lines of code by trend. As
				\crit{Containability}{3.3}, the modular independence (e.g.
				independence of the web interface from the Message Store file
				system) from a security perspective is perceived.

@@

		\todo{Sources for algorithms and their comparisons}

@@

			\begin{description}
				\item[\rm Managing domains, aliases and mailboxes]\ \\
					\todo

				\item[\rm Tested with postfix and dovecot]\ \\
					There are some productive installations of \emph{Møil} in
					connection with postfix and dovecot but it could possibly
					also be used with other mailing software which provides the
					opportunity to configure the \ac{SQL} statements used to
					request necessary meta data.

				\item[\rm Database agnostic]\ \\
					\emph{Møil} is tested mostly on SQLite3 and PostgreSQL but
					also occasionally on MySQL (or MariaDB respectively). In
					general, it should be supported on any database supported
					by \emph{Active Record}, which currently are (at least)
					MySQL, PostgreSQL, SQLite, SQL Server, Sybase, and all
					supported Oracle databases except
					DB2\footnote{\urlARSupport}.

@@

			The model connects to the \ac{DBMS} via TCP/IP or Unix Sockets. The
			abstractly noted queries are translated to the respective \ac{SQL}
			(or NoSQL) dialect. All communication with external services like
			postfix, dovecot or the relocation daemon (see
			\textref{sec:moeil:model:relocation}) happen solely with the
			\ac{DBMS} as an intermediary.

@@

			\subsubsection{Relevant configs for postfix and dovecot}
				The relevant configuration files for postfix and dovecot
				(especially regarding to the \ac{SQL} statements compatible to
				\emph{Møil}) can be found in the source code repository on
				GitHub in the folders
				\texttt{doc/postfix}\footnote{\url{https://github.com/nning/moeil/tree/master/doc/postfix}}
				and
				\texttt{doc/dovecot}\footnote{\url{https://github.com/nning/moeil/tree/master/doc/dovecot}}.

			\subsubsection{Setup of the rails app}
				The setup of the rails app for testing or deployment on
				OpenShift is described in the main
				README\footnote{\url{https://github.com/nning/moeil}} file of
				\emph{Møil}. A deployment in web servers like \emph{Apache},
				\emph{nginx} and \emph{lighttpd} is made similar to any other
				current \ac{Rails} project. (Also it is possible to deploy with
				\emph{capistrano}.) More detailed and beginner-friendly
				instructions will be provided in the main README file, later.

@@

	\newpage
	\section{Numbered index of criteria}
	\label{sec:appendix:criteria}
		\begin{easylist}
			& Data model
			&& Normalized schema
			&& \emph{postfix.admin} compatible
			&& \emph{postfix.admin} import
			&& Updatable (Migrations)
			&& Systematic database independence

			& Features
			&& Basic domain, mailbox and alias management
			&& Password changing for users
			&& Access control
			&& Others
			&&& Audit trail
			&&& Vacation
			&&& Sieve
			&&& Spam front-end

			& Security \& robustness
			&& Password hashing
			&& Test coverage
			&& Containability (e.g. independence of Message Store file system)

>>>>

	\begin{center}
		\textit{Updated versions of this document are to be found at \\
			\url{https://henning.orgizm.net/doc/moeil.pdf}.}
	\end{center}

@@

@@

			\subsubsection{Security \& robustness (3)}
				For now, only three criteria in this category shall be
				considered, because further security analysis would require an
				in-depth source code review. The \crit{password hashing}{3.1}
				availability and algorithm strength is important against
				unauthorized database access through potential security holes
				in the application. When the database is maliciously read, the
				value of the passwords to the attacker is inversely
				proportional to the time it costs, to crack the password
				hashing. \texttt{MD5} and \texttt{SHA1} based methods are
				considered unsecure, \texttt{SHA256}, \texttt{SHA384},
				\texttt{SHA512} and \texttt{bcrypt} are
				recommended\footnote{\url{http://www.keylength.com/en/8/}}.
				\crit{Test coverage}{3.2} is important for this evaluation and
				for security purposes, because it lowers the probability of
				bugs per lines of code by trend. As \crit{Containability}{3.3},
				the modular independence (e.g. independence of the web
				interface from the Message Store file system) from a security
				perspective is perceived.

@@

@@

			\begin{description}
				\item[\rm Managing domains, mailbox and aliases]\ \\
					\emph{Møil} provides beautiful and usable \acp{UI} for
					management tasks on domains, mailboxes and aliases hosted
					on a mail system.

				\item[\rm Tested with \emph{postfix} and \emph{dovecot}]\ \\
					There are some productive installations of \emph{Møil} in
					connection with \emph{postfix} and \emph{dovecot} but it
					could possibly also be used with other mailing software
					which provides the opportunity to configure the \ac{SQL}
					statements used to request necessary meta data.

				\item[\rm Database agnostic]\ \\
					\emph{Møil} is tested mostly on \emph{SQLite3} and
					\emph{PostgreSQL} but also occasionally on \emph{MySQL} (or
					\emph{MariaDB} respectively). In general, it should be
					supported on any database supported by \emph{Active
					Record}, which currently are (at least) \emph{MySQL},
					\emph{PostgreSQL}, \emph{SQLite}, \emph{SQL Server},
					\emph{Sybase}, and all supported Oracle databases except
					\emph{DB2}\footnote{\urlARSupport}.

@@

			The model connects to the \ac{DBMS} via TCP/IP or Unix Sockets. The
			abstractly noted queries are translated to the respective \ac{SQL}
			(or NoSQL) dialect. All communication with external services like
			\emph{postfix}, \emph{dovecot} or the relocation daemon (see
			\textref{sec:moeil:model:relocation}) happen solely with the
			\ac{DBMS} as an intermediary.

@@

			\subsubsection{Relevant configs for \emph{postfix} and \emph{dovecot}}
				The relevant configuration files for \emph{postfix} and
				\emph{dovecot} (especially regarding to the \ac{SQL} statements
				compatible to \emph{Møil}) can be found in the source code
				repository on GitHub in the folders
				\texttt{doc/postfix}\footnote{\url{https://github.com/nning/moeil/tree/master/doc/postfix}}
				and
				\texttt{doc/dovecot}\footnote{\url{https://github.com/nning/moeil/tree/master/doc/dovecot}}.

			\subsubsection{Setup of the rails application}
				The setup of the rails app for testing or deployment on
				OpenShift is described in the main
				README\footnote{\url{https://github.com/nning/moeil}} file of
				\emph{Møil}. A deployment in web servers like \emph{Apache},
				\emph{nginx} and \emph{lighttpd} is made similar to any other
				current \ac{Rails} project. (Also it is possible to deploy with
				\emph{capistrano}.) More detailed and beginner-friendly
				instructions will be provided in the main README file at a
				later point.

@@

	\newpage
	\section{Numbered index of criteria}
	\label{sec:appendix:criteria}
		\begin{easylist}
			& Data model
			&& Normalized schema
			&& \emph{postfix.admin} compatible
			&& \emph{postfix.admin} import
			&& Schema migrations
			&& Systematic database independence
			\s

			& Features
			&& Basic domain, mailbox and alias management
			&& Password changing for users
			&& Access control
			&& Others
			&&& Audit trail
			&&& Vacation
			&&& Sieve
			&&& Spam front-end
			\s

			& Security \& robustness
			&& Password hashing
			&& Test coverage
			&& Containability
			\s
